---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# nlss

<!-- badges: start -->
<!-- badges: end -->

Network Latent Source Separation (NLSS), a blind source separation algorithm designed for network data.

## Installation

Install the released version of nlss from Github with:

``` r
devtools::install_github("benwu233/nlss")
```


## Example

This is a basic example shows the implement of nlss package:


Load the package and generate three true latent source networks. 
```{r, message=FALSE, warning=FALSE}
library(nlss)  
set.seed(716)
signal = gen_sources(100)
```

Draw the true sources.
```{r, message=FALSE, fig.keep='last', fig.height = 2.2}
library(gplots)
heatmap.net(signal$S,lim=c(0,1),
             community = signal$community,
             color = colorpanel(n = 100, low = "white", high = "black"))
```


Generate network data with NLSS.
```{r, message=FALSE}
sim0 = sim_NLSS(n = 150, alpha_0 = c(0.8,0.8,0.8),
                         alpha_1 = 0.8, sd0 = 0.25, signal$S)
```


Draw samples of the network data.
```{r, message=FALSE, fig.keep='last', fig.height = 2.2}
heatmap.net(sim0$Xc[1:3,],lim=c(0,1),
             community = signal$community,
             color = colorpanel(n = 100, low = "white", high = "black"))
```


Solve with the MCMC algorithm:
```{r}
data0 = thr_byrow(sim0$Xc,0.1)
res = NLSS(data=data0, q=3, states = c(0,1), state0 = 0,
                      total_iter = 2000, burn_in = 0, thin = 10,
                      show_step=1000, joint=TRUE,
                      q0 = 3)
```

Summarize the results:
```{r}
sum_res = NLSS_sum(res,th=0.95, nstart = 1, nend = 100)
```

Print the estimated source networks:
```{r, message=FALSE, fig.keep='last', fig.height = 2.2}
heatmap.net(sum_res$S,lim=c(0,1),
             community = signal$community,
             color = colorpanel(n = 100, low = "white", high = "black"))
```

Match and compare with the true sources:
```{r}
S_match = match_source(signal$S, sum_res$S)
lapply(1:3, function(i){caret::confusionMatrix(as.factor(S_match[i,]), as.factor(signal$S[i,]), positive = "1" )} )
```

